=enter title here=

### 2021-08-10 paper/agujournaltemplate.tex
Write methods

In this study, we use wavelet methods to analyze GPS and seismic recordings of slow slip events in Cascadia. Our objective is to verify that there is a good correlation between slow slip events detected with only GNSS data, and slow slip events detected with only seismic data. We thus want to demonstrate that the wavelet-based detection method can be applied to detect possible smaller (magnitude 5) slow slip events that may be currently undetected with standard methods. \\

@@

>>>>

In this study, we use wavelet methods to analyze GPS and seismic recordings of slow slip events in Cascadia. Our objective is to verify that there is a good correlation between slow slip events detected with only GNSS data, and slow slip events detected with only seismic data. We thus want to demonstrate that the wavelet-based detection method can be applied to detect slow slip events that may be currently undetected with standard methods. \\

@@

We then applied the wavelet filtering to real GPS data. Figure 2 shows the longitudinal displacement for GPS station PGC5, located in southern Vancouver Island, the details of the wavelet decomposition for levels 1 to 8, and the smooth. In the data, we can see a sharp drop in displacement whenever there is a slow slip event. For levels 5 to 8, we can see in the details a positive peak followed by a negative peak whenever there is a drop in displacement in the data. We thus verify that the wavelet method can detect slow slip events. \\

\begin{figure}
\noindent\includegraphics[width=5cm, trim={0cm 0cm 0cm 0cm},clip]{figures/cleaned_PGC5_lon.eps}
\caption{Details and smooth of the wavelet decomposition of the longitudinal displacement recorded at GPS station PGC5.}
\label{pngfiguresample}
\end{figure}

To increase the signal-to-noise ratio and be able to better detect slow slip events, we stack the signal over several GPS stations. We choose to focus on GPS stations located close enough to the tremor zone to get a sufficiently high amplitude of the slow slip signal. We choose 16 points located on the 40 km depth contour of the plate boundary (model from ~\citet{PRE_2003}) with spacing equal 0.1 degree in latitude (red triangles on Figure 3). Then we took all the GPS stations located in a 50 km radius for a given point, compute the wavelet details for the longitudinal displacement of each station, and stack each detail over the GPS stations. We thus have a stacked detail for each level 1 to 8 of the wavelet decomposition. \\

\begin{figure}
\noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/map_GPS_stations.eps}
\caption{GPS stations used in this study (black triangles). The black line represents the 40 km depth contour of the plate boundary model by ~\citet{PRE_2003}. The red triangles are the locations where we stack the GPS data. The small grey dots are all the tremor locations from the PNSN catalog.}
\label{pngfiguresample}
\end{figure}

To compare slow slip events detected with GPS data and slow slip events detected with seismic data, we took all the tremor epicenters located within a 50 km radius centered on one of the 16 locations marked by red triangles on Figure 3. Then we computed the cumulative number of tremor within this circle. Finally, we removed a linear trend from the cumulative tremor count, and applied the wavelet transform. Figure 4 shows an example of the wavelet decomposition for the third northernmost location on Figure 3 (which is closest to GPS station PGC5). Contrary to what happens for the GPS data, we see a sharp increase in the data whenever there is a tremor episode, which translates into a negative peak followed by a positive peak in the wavelet details.

\begin{figure}
\noindent\includegraphics[width=5cm, trim={0cm 0cm 0cm 0cm},clip]{figures/tremor_13.eps}
\caption{Details and smooth of the wavelet decomposition of the detrended cumulative tremor count around the third northernmost location on Figure 3.}
\label{pngfiguresample}
\end{figure}
